\section{Free groups, free products, generators and relations}
\begin{ex}
    Every nonidentity elements in a free group $F$ has a infinite order.
\end{ex}

\begin{answer}
    Define the length of a word $x=a_{1}^{\lambda_{1}}a_{2}^{\lambda_{2}}\cdots a_{n}^{\lambda_{n}}$ is $n$ and denote it as $len(x)$. Assume $len(x)=n$ for some $n\in F$ and $len(1)=0$, we prove that $len(x^{m})\geq n\forall m\geq 1$.

    Let $k$ be the largest integer such that  $a_{n-j}^{\lambda_{n-j}}=a_{n}^{-\lambda_{j}}$ for $j=0, 1, \dots, k-1$. If $k>\left[\frac{n}{2}\right]$. For even $k$, $a_{\frac{n}{2}}^{\lambda_{\frac{n}{2}}}=a_{\frac{n}{2}+1}^{-(\lambda_{\frac{n}{2}+1})}$, $a_{\frac{n}{2}-1}^{\lambda_{\frac{n}{2}-1}}=a_{\frac{n}{2}+2}^{-(\lambda_{\frac{n}{2}+2})}$, $\cdots$ which means $x=a_{1}^{\lambda_{1}}a_{2}^{\lambda_{2}}\cdots a_{n}^{\lambda_{n}}=1$. For odd $k$, $a_{\left[\frac{n}{2}\right]+1}^{\lambda_{\left[\frac{n}{2}\right]+1}}=a_{\left[\frac{n}{2}\right]+1}^{-(\lambda_{\left[\frac{n}{2}\right]+1})}$, which is contradictory to $x$ is reduced. So $k\leq \left[\frac{n}{2}\right]$.

    Divide $x=x_{1}x_{2}x_{3}$ where $x_{1}=a_{1}^{\lambda_{1}}\cdots a_{k}^{\lambda_{k}}$, $x_{2}=a_{k+1}^{\lambda_{k+1}}\cdots a_{n-k}^{\lambda_{n-k}}$, $x_{3}=a_{n-k+1}^{\lambda_{n-k+1}}\cdots a_{n}^{\lambda_{n}}$. $x_{3}x_{1}=1$. So $len(x)=len(x_{1})+len(x_{2})+len(x_{3})=n$. $x^{m}=x_{1}x_{2}x_{3}x_{1}x_{2}x_{3}\cdots x_{1}x_{2}x_{3}=x_{1}x_{2}^{m}x_{3}$. $len(x^{m})=len(x_{1})+m\cdot len(x_{2})+len(x_{3})\geq n$. So $\forall m\geq 1$, $x^{m}\neq 1$, $\left| x \right| $ is infinite.
\end{answer}

$$ $$

\begin{ex}
    Show that the free group on the set $\{a\}$ is an infinite cyclic group, and hence isomorphic to $\mathbf{Z}$.
\end{ex}

\begin{answer}
    $F(\{a\})=\left\langle a\right\rangle$ and thus it's a infinite cyclic group. $F(\{a\})\cong \mathbf{Z}$.
\end{answer}

$$ $$

\begin{ex}
    Let $F$ be a free group and let $N$ be the subgroup generated by the set $\{x^{n}|x\in F, n\text{ a fixed integer}\}$. Show that $N\lhd F$.
\end{ex}

$$ $$

\begin{ex}
    Let $F$ be the free group on the set $X$, and let $Y\subset H$. If $H$ is the smallest normal subgroup of $F$ containin $Y$, then $F /H$ is a free group.
\end{ex}

$$ $$

\begin{ex}
    The group defined by generators $a,b$ and relations $a^{8}=b^{2}a^{4}=ab^{-1}ab=e$ has order at most 16.
\end{ex}

$$ $$

\begin{ex}
    The cyclic group of order 6 is the group defined by generators $a, b$ and relations $a^{2}=b^{3}=a^{-1}b^{-1}ab=e$.
\end{ex}

$$ $$

\begin{ex}
    Show that the group defined by generators $a, b$ and relations $a^{2}=e$, $b^{3}=e$ is infinite and nonabelian.
\end{ex}

$$ $$

\begin{ex}
    The group defined by generators $a, b$ and relations $a^{n}=e (3\leq n\in \mathbf{N}^{*})$, $b^{2}=e$ and $abab=e$ is the dihedral group $D_{n}$.
\end{ex}

$$ $$

\begin{ex}
    The group defined by the generator $b$ and $b^{m}=e(m\in \mathbf{N}^{*})$ is the cyclic group $Z_{m}$.
\end{ex}

$$ $$

\begin{ex}
    The operation of free product is communicative and associative: for any groups $A$, $B$, $C$, $A*B\cong B*A$ and $A*(B*C)\cong (A*B)*C$.
\end{ex}

$$ $$

\begin{ex}
    If $N$ is normal subgroup of $A*B$ generated by $A$, then $(A*B) /N\cong B$.
\end{ex}

$$ $$

\begin{ex}
    If $G$ and $H$ each have more than one element, then $G*H$ is an infinite group with center $\left\langle e\right\rangle$.
\end{ex}

$$ $$

\begin{ex}
    A free group is a free product of infinite cyclic groups.
\end{ex}

$$ $$

\begin{ex}
    If $G$ is the group defined by generators $a, b$ and relations $a^{2}=e$, $b^{3}=e$, then $G\cong Z_{2}*Z_{3}$.
\end{ex}

$$ $$

\begin{ex}
    If $f:G_{1}\to G_{2}$ and $g:H_{1}\to H_{2}$ are homomorphisms of groups, then there is a unique homomorphism $h:G_{1}*H_{1}\to G_{2}H_{2}$ such that $h|G_{1}=f$ and $h|H_{1}=g$.
\end{ex}